Research Proposal: Specialization Trends in Economics Research using JEL Codes \\ Text Data in Economics by Aapo Stenhammar \\ University of Bonn, Winter Term 2024/25

### 2025-02-21 documents/paper.tex
Data analysis preparation and initital plot.
Renaming and refactoring of structure.

\title{Reproduction and Expansion of \\"SPECIALIZATION TRENDS IN ECONOMICS RESEARCH" by Sebastian Galiani, Ramiro H. Gálvez, and Ian Nachman}

\author{Felix Schmitz}

\date{
    {\bf Under construction}
    \\[1ex]
    \today
}

@@

>>>>

\title{Research Proposal: Specialization Trends in Economics Research using JEL Codes \\
Text Data in Economics by Aapo Stenhammar \\
University of Bonn, Winter Term 2024/25}

\author{Felix Schmitz\footnotemark[1]}

\date{
    \today
}

@@

\subsection{Data Collection and Cleaning}
For the analysis only data between January 2000 and December 2024 was selected.
This is mainly to ensure a sufficient number of observations per month (for the early years) and complete information on the discussion paper (for the most recent discussion papers).
This reduces the sample size by 195 observations. The final number of discussion papers analysed is 17,449.

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{../bld/figures/fig_counts_avg_jel_codes}
    \caption{Discussion Papers \& Avg. JEL Codes per Paper Over Time}
    \label{fig:monthly_counts_and_avg_jel_codes_per_paper}
\end{figure}
